### 2024-09-26 manuscript.tex
Various improvements

The relationship between cloud biases and radiation has a number of notable
features. Perhaps unsurprisingly, The reanalyses exhibit the too few,
too bright type of bias previously identified in models. In our results,
this is characterised by outgoing SW radiation similar to or higher
than in satellite observations, while at the same time total cloud fraction
is substantially underestimated relative to the ground-based lidar observation.
This feature seems to be much more pronounced in ERA5 than in MERRA-2. On
the other hand, this type of relationship is not present in ICON. This model
mostly predicts smaller outgoing SW radiation and smaller total cloud fraction
than observations, and the deficit of outgoing SW radiation is approximately
proportial to the deficit of the total cloud fraction. While this might be a
welcome feature and an improvement over previous models, it does mean that the
outgoing SW radiation is overall underestimated, instead of being compensated
by a higher cloud albedo. This can, of course, lead to undesirable secondary
effects such as overestimated solar heating of the sea surface, but a
combination of many factors have been found to be responsible for SO SST biases
in climate models \citep{zhang2023,luo2023}.

@@

We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
Institute and Pangaea, RSV \emph{Aurora Australis} datasets provided by the
Australian Antarctic Program and the University of Canterbury (UC), RV
\emph{Tangaroa} datasets provided by the National Institute of Water and
Atmospheric Research and the UC, RV \emph{Nathaniel B. Palmer} dataset provided
by the National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and the UC, HMNZS
\emph{Wellington} dataset provided by the Royal New Zealand Navy and the UC and
the Macquarie Island station dataset provided by the Atmospheric Radiation
Measurement and the UC.  We thank the scientific staff, the crew, and everyone
involved in collecting data on the voyages and stations, especially Kelly
Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey, Simon P.  Alexander and
Alex Schuddeboom. We acknowledge the ICON model output provided by the
Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5 provided by the
Copernicus Climate Change Service and MERRA-2 provided by the Global Modeling
and Assimilation Office.

>>>>

The relationship between cloud biases and radiation has a number of notable
features. Perhaps unsurprisingly, the reanalyses exhibit the too few, too
bright bias previously identified in models. In our results, this is
characterised by outgoing TOA SW radiation similar to or higher than in
satellite observations, while at the same time total cloud fraction is
substantially underestimated relative to the ground-based lidar observation.
This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
other hand, this type of relationship is not present in ICON. This model mostly
predicts smaller outgoing TOA SW radiation and smaller total cloud fraction
than observations, and the deficit of outgoing TOA SW radiation is
approximately proportial to the deficit of the total cloud fraction. While this
might be a welcome feature and an improvement over previous models, it does
mean that the outgoing TOA SW radiation is overall underestimated, instead of
being compensated by a higher cloud albedo. This can, of course, lead to
undesirable secondary effects such as overestimated solar heating of the sea
surface. Previously, a combination of many factors have been found to be
responsible for SO SST biases in climate models \citep{zhang2023,luo2023}.

@@

We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
Institute and Pangaea, RSV \emph{Aurora Australis} datasets provided by the
Australian Antarctic Program and the University of Canterbury (UC), RV
\emph{Tangaroa} datasets provided by the National Institute of Water and
Atmospheric Research and the UC, RV \emph{Nathaniel B. Palmer} dataset provided
by the National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and the UC, HMNZS
\emph{Wellington} dataset provided by the Royal New Zealand Navy and the UC and
the Macquarie Island station dataset provided by the Atmospheric Radiation
Measurement and the UC.  We thank the scientific staff, the crew, and everyone
involved in collecting data on the voyages and stations, especially Kelly
Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander and
Alex Schuddeboom. We acknowledge the ICON model output provided by the nextGEMS
project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5
provided by the Copernicus Climate Change Service and MERRA-2 provided by the
Global Modeling and Assimilation Office. We would like to dedicate this study
to the memory of Mike J. Harvey, who very substantially contributed to
obtaining atmospheric measurments on the RV \emph{Tangaroa} voyages used in
this study.
